Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-10-07 referee.tex
Adjusted some comments - but finalized my comments to the referee.

There was an error in the original draft of our paper, stating that "If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells." It should instead say "within 10 pc", not "within 1 pc". This error has been corrected.

@@

@@

We apologize for not being more clear on this point.  As seen in Figure \ref{fig:compare_mass}, there are seven stars that form in a halo with $M_{\rm halo} > 10^8 M_\odot$ but are actually hosted by a subhalo that hasn't been enriched yet.  This is an interesting case within itself.  We might follow up on this object in a later study because it's outside the scope of the paper.  Because we take the parent halo mass as the host halo mass, we did not include these stars in the analysis because the parent halo mass is not representative of the cooling processes inside of the subhalo.  Because this is a rare event in our simulation (7 out of 688 Pop III stars), it does not shift the average halo mass by a significant amount.  We have added some clarifying text to the first paragraph of the Section 3.1.

@@

\jhw{This is good.}

@@

In Hartwig+15, they take into account the Doppler-shifting of spectral lines with an improved calculation of the column densities, but use the same shielding factor as we do. They find that shielding is generally less efficient at higher temperatures. In our work, because our halos are less massive, the temperatures are typically $10^{3}$ K, which looking at the Figure 5, lies close to the 1:1 line. The shielding factor as calculated in our work will therefore not vary significantly compared to the full treatment of the column density, so we do not expect this to be a problem.

@@

\begin{referee}
W -- One of the most extensive studies on over 1000 minihaloes was performed by Hirano+15, who also include a Lyman-Werner background. Their work should be put in comparison as well.
\end{referee}
This study has been added and cited in the Comparison section.
-Should more be added?

>>>>

There was an error in the original draft of our paper, stating that ``If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells." It should instead say ``within 10 pc", not ``within 1 pc". This error has been corrected.

@@

--May still need to answer the questions ``Which is the motivation for the length scale of 1 pc?''

@@

We apologize for not being more clear on this point.  \textbf{As seen in Figure \ref{fig:compare_mass}, there are seven stars that form in a halo with $M_{\rm halo} > 10^8 M_\odot$ but are actually hosted by a subhalo that hasn't been enriched yet. \textit{DS -- this figure was removed for simplicity}} This is an interesting case within itself.  We might follow up on this object in a later study because it's outside the scope of the paper.  Because we take the parent halo mass as the host halo mass, we did not include these stars in the analysis because the parent halo mass is not representative of the cooling processes inside of the subhalo.  Because this is a rare event in our simulation (7 out of 688 Pop III stars), it does not shift the average halo mass by a significant amount.  We have added some clarifying text to the first paragraph of the Section 3.1.

@@

@@

In Hartwig+15, they take into account the Doppler-shifting of spectral lines with an improved calculation of the column densities, but use the same shielding factor as we do. They find that shielding is generally less efficient at higher temperatures. In our work, because our halos are less massive, the temperatures are typically $10^{3}$ K, which looking at their Figure 5, lies close to the 1:1 line. The shielding factor as calculated in our work will therefore not vary significantly compared to the full treatment of the column density, so we do not expect this to be a problem.

@@

\begin{referee}
W -- One of the most extensive studies on over 1000 minihaloes was performed by Hirano+15, who also include a Lyman-Werner background. Their work should be put in comparison as well.
\end{referee}
This study has been added and cited in the Comparison section.
\textbf{-Should more be added?}
